Predicting FOMC Actions using ML and NLP

### 2019-05-04 presentation/paper.tex
update

    \item Naive Bayes
    \item Logistic Regression
    \item Logistic Lasso
    \item SVM
    \item Neural Network

  \end{itemize}

@@

In addition, because this is a binary classification problem, we also exptected Logistic Regression with L1 penalty (i.e., Logistic Lasso) to perform better than Logistic Regression with L2 regularization.  \vertSpace

We included Naive Bayes as a benchmark due to prior study of FOMC sentiment analysis using NLP found that Naive Bayes perfomed the best in their study.

@@

\begin{figure}[h!]
\centering
\begin{subfigure}{.5\textwidth}
  \centering
\includegraphics[height=2in,width=2in]{../text/data_for_graphs/accuracy.pdf}
\caption{Accuracy peaks at around 10 iterations}
\end{subfigure}%
\begin{subfigure}{.5\textwidth}
  \centering
\includegraphics[height=2in,width=2in]{../text/data_for_graphs/F1.pdf}
  \caption{A subfigure}
  \label{fig:sub2}
\end{subfigure}
\caption{F1 also peaks at around 10 iterations}
\label{fig:test}
\end{figure}

>>>>

    \item Naive Bayes

      $$P(A|x_1,x_2,...,x_n) = p(A)\prod_{i=1}^n p(x_i|A)$$

    \item Logistic Regression

     $$A = \prod_{i=1}^n p(x_i)^{y_i}(1-p(x_i))^{1-y_i}$$

    \item Logistic Lasso
     $$A = \prod_{i=1}^n p(x_i)^{y_i}(1-p(x_i))^{1-y_i}+ L1$$
    \item SVM

     $$\left [\frac{1}{n} \sum_{i=1}^n max(0,1 - y_i(\vec{w} \dot \vec{x_i} - b)) \right] + \lambda ||\vec{w}||^2$$
    \item Neural Network
      We test a mixture of wide and deep neural nets. 
  \end{itemize}

@@

In addition, because this is a binary classification problem, we also exptected Logistic Regression with L1 penalty (i.e., Logistic Lasso) to perform better than Logistic Regression without any regularization.  \vertSpace

Given that we are modelling a classification problem, we would expect the performance of the Logistic Lasso model based on the mathematical properties of Logistic Lasso more robust for predicting FOMC rate action.  Logistic regression models the probability distribution of the class label $y$ given a feature vector $x$:

$$p(y=1|x,\theta) = \sigma(\theta^T x) = \frac{1}{1+\exp(-\theta^Tx)}$$

The L1 regularized logistic regression (Logistic Lasso) is defined as:

$$\underset{\rm \theta}{\rm min} \sum_{i=1}^M -\log p(y^{(i)}|x^{(i)}; \theta) + \beta ||\theta||$$

L1 regularization has the effect of forcing feature selection, and as we observe the Logistic Lasso model performs best Tri-grams to 7-grams and performance significantly drops with larger Ngrams.  \vertSpace

Below is the average accuracy of the four basic classifiers (Naive Bayes, SVM, Logistic Regression, and Logistic Lasso) after 10 iterations:

\begin{figure}[h!]
\begin{center}
\includegraphics[width=.3\textwidth]{"../output/data_for_graphs/log_lass_accuracy_more iterations".pdf}
\includegraphics[width=.3\textwidth]{"../output/data_for_graphs/log_reg_accuracy_more iterations".pdf}
\includegraphics[width=.3\textwidth]{"../output/data_for_graphs/NB_accuracy_more iterations".pdf}
\includegraphics[width=.3\textwidth]{"../output/data_for_graphs/SVM_accuracy_more iterations".pdf}
\end{center}
\end{figure}

\vspace{5cm}

@@

\begin{figure}[h!]
\begin{center}
\includegraphics[width=.3\textwidth]{"../output/data_for_graphs/log_lasso_f1".pdf}
\includegraphics[width=.3\textwidth]{"../output/data_for_graphs/log_f1".pdf}
\includegraphics[width=.3\textwidth]{"../output/data_for_graphs/naive_bayes_f1".pdf}
\includegraphics[width=.3\textwidth]{"../output/data_for_graphs/SVM_f1".pdf}
\end{center}
\end{figure}
